SDR enhancement by clouds

### 2024-03-19 article/article.Rmd
Commit 2024-03-19 12:14

The recording of the signal is the one minute average.
Thus we will refer to this time scale as a cloud enhancement event (CE).

@@

Furthermore, to account for the Sun's variability in our one-minute GHI measurements,
we adjusted the model's input spectrum integral to the one of the the TSI provided by
NOAA.  Finally, we adjusted for the effect of the Sun - Earth distance, and
calculated the clear sky irradiance value at the horizontal plane by using the cosine
of the corresponding interpolated SZA.  For each period of the year, we used the
appropriate atmospheric profile (afglms or afglmw).  Thus, the modelled GHI_modeld we
can directly compare each measured one minute value of GHI, with the expected clear
sky radiation.

@@

After some evaluation of the modelled radiation in different atmospheric conditions, in relation to the GHI data, we choose as representative of the clear sky radiation, the case with $t_{\text{cs}} = t_{500\text{nm}} - 1\sigma$ and $w_{h\text{cs}} = w_h - 1\sigma$.

@@

```{r P-energy-N, echo=FALSE, fig.cap="Trend of yearly CE number of occurancies."}
knitr::include_graphics("../images/P_energy-6.png")
```
Subsequently, the annual energy observed during CE events shows a annual increase of
$`r round(yearlyCE[var == "GLB_diff.sum", slope], 1)`\pm
`r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,kJ/y$
(Figure\ \ref{fig:P-energy-sum}).

@@

```{r echo=FALSE, fig.cap="Distribution of the number of CE cases"}
knitr::include_graphics("../images/climCEmonth-1.png")
```

@@

```{r echo=FALSE, fig.cap="Distribution of "}
knitr::include_graphics("../images/clim_CE_month_norm_MAX_median_N-2.png")
```

>>>>

The recording of the signal is the one-minute average.
Thus we will refer to this time scale as a cloud enhancement event (CE).

@@

Furthermore, to account for the Sun's variability in our one-minute GHI measurements,
we adjusted the model's input spectrum integral to the one of the the TSI provided by
NOAA.  Finally, we adjusted for the effect of the Sun - Earth distance, and
calculated the clear sky irradiance value at the horizontal plane by using the cosine
of the corresponding interpolated SZA.  For each period of the year, we used the
appropriate atmospheric profile (afglms or afglmw).  Thus, the modeled GHI_modeled we
can directly compare each measured one minute value of GHI, with the expected clear
sky radiation.

@@

After some evaluation of the modeled radiation in different atmospheric conditions,
in relation to the GHI data, we choose as representative of the clear sky radiation,
the case with
$t_{\text{cs}} = t_{500\text{nm}} - 1\sigma$ and $w_{h\text{cs}} = w_h - 1\sigma$.

@@

```{r P-energy-N, echo=FALSE, fig.cap="Trend of yearly CE number of occurancies."}
knitr::include_graphics("../images/P_energy-6.png")
```
Subsequently, the annual energy observed during CE events shows a annual increase of
$`r round(yearlyCE[var == "GLB_diff.sum", slope], 1)`\pm
`r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,kJ/y$
(Figure\ \ref{fig:P-energy-sum}), witch follows the trend of the number of
occurrences.

@@

Another interesting aspect of the CE cases, is the seasonal cycle. In Figure\ 
\ref{fig:relative-month-occurancies}, we have the box plot (whisker plot), where the
values have been normalized by the highest median value, that occurs in May.
Although the number of occurrences has a wide spread throughout the study period,
the most active period of CE occurrences is during May and June. During the Winter
(December -- February) the CE cases are about 25% of the maximum. The rest of the
months the occurrences seems to ramp between the maximum and minimum.

```{r relative-month-occurancies, echo=FALSE, fig.cap="Statistics of the number of CE occurancies for each month. The box represents the values of the low 25% percentile to 75% percentile, where the thick horizontal line inside is the mean, the verical lines extend to the macimum and minimum vales, the dots are outlier values, and the rhombus is the mean."}
knitr::include_graphics("../images/clim_CE_month_norm_MAX_median_N-2.png")
```

mean rhombus

<!--
```{r echo=FALSE, fig.cap="Distribution of the number of CE cases"}
knitr::include_graphics("../images/climCEmonth-1.png")
```
--->

@@
